Synthesizing Quotient Lenses

### 2018-03-09 papers/QuotientLenses/main.tex
Checkpoint

{\em Quotient lenses} loosen many of the restrictions of bijective lenses by
allowing a programmer to define an equivalence relation on the source and
target formats so that the round-tripping lens laws hold modulo these
equivalence rather than modulo equality. Quotient lenses thus make it possible
to align many more data sources than would otherwise be possible, by ignoring
details that a programmer views as inessential. The only language we are aware
of that implements a general class of quotient lenses is {\em
Boomerang}~\cite{quotientlenses}. While Boomerang's quotient lenses enable a
programmer to define a very general class of quotient lenses, these lenses to
have two main drawbacks.

@@

We have implemented QREs and the quotient lens synthesis algorithm described
above as part of Boomerang. Thanks to this integration, QREs and quotient lens
synthesis tasks can now be expressed alongside existing Boomerang terms, and we
can combine the two kinds of lenses seamlessly in the same application.
Intuition suggests that the increased expressiveness of QREs should make many
lens programming tasks easier, but we would like more quantitative understanding
of that claim.  We thus conducted several experiments that aim to provide
answers to the following questions:

>>>>

{\em Quotient lenses} loosen many of the restrictions of bijective lenses by
allowing a programmer to define an equivalence relation on the source and
target formats so that the round-tripping lens laws hold modulo these
equivalence rather than modulo equality. Quotient lenses thus make it possible
to align many more data sources than would otherwise be possible, by ignoring
details that a programmer views as inessential. The only language we are aware
of that implements a general class of quotient lenses is {\em
Boomerang}~\cite{quotientlenses}\bcp{Is this the right citation for
Boomerang?  Or should it be \cite{boomerang}?}. While Boomerang's quotient
lenses enable a 
programmer to define a very general class of quotient lenses\bcp{read
  literally, that part of the sentence is nonsense: boomerang's lenses
  (themselves) do not enable the programmer to define lenses.  Of course,
  the reader can probably figure out what is meant, but that's a needless
  tax on their finite mental energy.}, these lenses to have two main
drawbacks.

@@

We have implemented QREs and the quotient lens synthesis algorithm described
above as an extension to the Boomerang interpreter~\cite{Boomerang}. Thanks to this integration, QREs and quotient lens
synthesis tasks can now be expressed alongside existing Boomerang terms, and we
can combine the two kinds of lenses seamlessly in the same application.
Intuition suggests that the increased expressiveness of QREs should make many
lens programming tasks easier, but we would like more quantitative understanding
of that claim.  We thus conducted several experiments that aim to provide
answers to the following questions:
